---
title: "PAC_FINAL"
author: "Zeeshan"
date: "4/30/2022"
output:
  html_document: default
  pdf_document: default
---
#REQUIRED PACKAGES
```{r}
library(imputeTS)
library(tidyverse)
library(dplyr)
library(lubridate)
library(skimr)
library(rpart)
library(caret)
library(xgboost)
library(randomForest)
library(lattice)
names(df)
```


#DATA LOADING
```{r}
df = read_csv("/Users/zee/Documents/PACE ACADEMICS/Spring 2022/Predictive Analytics/predictrentlala2022/analysisData.csv")
scoringdata=read_csv("/Users/zee/Documents/PACE ACADEMICS/Spring 2022/Predictive Analytics/predictrentlala2022/scoringData.csv")
data_n = df
```


```{r}
dim(data_n)
```
```{r}
skimr::skim(data_n)
```

#DATA EXPLORTION
```{r}
ggplot(df,aes(x=room_type,fill=room_type))+geom_bar(color="black")+
  labs(title = "Types of Rooms at AIRBNB", x= "Type of Rooms", y = "Count")+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
ggplot(df,aes(x=mean(price),y=neighbourhood_group_cleansed,fill=room_type)) + geom_bar(stat='identity') +  
  labs(title = "Avg Price within NYC for respective Room type", x= "Price", y = "Neighbourhood")+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
ggplot(df,aes(x=accommodates,y=price,color=neighbourhood_group_cleansed)) + geom_point() + geom_smooth()+
  facet_wrap(~neighbourhood_group_cleansed)+
  labs(title = "Price Vs Accomodates in Respective Counties", x= "Accommodates", y = "Price")+scale_x_continuous()+
  scale_y_continuous() + theme(plot.title = element_text(hjust = 0.7))
```

```{r}
ggplot(df,aes(x=price,y=availability_30))+geom_point(color="yellow",
        fill="#fd90c8",
        shape=23,
        alpha=0.7,
        size=3,
        stroke = 1, aes(text = paste("Price:", price, "<br>",
                     "Availability:", availability_30)))+
  geom_smooth()+
  scale_y_continuous(limits = c(0,40))+
  scale_x_continuous()+
  labs(title = "Price and Availability in month", x= "Price", y = "Availability")+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
```
DATA CLEANING !!!

#Removal of Character features for Model Building!!
```{r}
a = sapply(data_n,is.character) %>% which(data_n==TRUE)    #'*SAPPLY FUNCTION FOR INCLUDING ALL CHARACTER VARIABLES FOR REMOVAL*
data_n = subset(data_n, select =-c(a))
data_n = subset(data_n, select =-c(first_review,last_review))     
data_n= subset(data_n,select=-c(license,jurisdiction_names))
data_n= subset(data_n,select=-c(weekly_price,monthly_price))
data_n= subset(data_n,select=-c(square_feet))
data_n = subset(data_n,select= -c(host_since))
skim(data_n)
```

#TRANFORMING DATA INTO 0 AND 1 FOR THE LOGICAL VARAIBLE
```{r}
data_n$is_location_exact=as.integer(data_n$is_location_exact)
data_n$host_identity_verified = as.integer(data_n$host_identity_verified)
data_n$is_business_travel_ready = as.integer(data_n$is_business_travel_ready)
data_n$instant_bookable = as.integer(data_n$instant_bookable)
data_n$host_has_profile_pic = as.integer(data_n$host_has_profile_pic)
data_n$host_is_superhost = as.integer(data_n$host_is_superhost)
data_n$has_availability = as.integer(data_n$has_availability)
data_n$requires_license = as.integer(data_n$requires_license)
data_n$require_guest_profile_picture = as.integer(data_n$require_guest_profile_picture)
data_n$require_guest_phone_verification = as.integer(data_n$require_guest_phone_verification)
skim(data_n)
```
#Imputation of mean on the missing values!

```{r}
data_n = na_mean(data_n)  #use of Package ImputeTS 
skim(data_n)
```

```



SPLITING DATA 
```{r}
library(caret)
set.seed(1031)
split = createDataPartition(y = data_n$price, p = 0.75, list = F, groups = 100)
train = data_n[split,]
test =  data_n[-split,]
```

FEATURE SELECTION!
```{r}
start_mod = lm(price~1,data=train)
empty_mod = lm(price~1,data=train)
full_mod = lm(price~.,data=train)
hybridStepwise2 = step(start_mod,
                      scope=list(upper=full_mod,lower=empty_mod),
                      direction='both')

#TRAIN DATA FEATURE SELECTION
train = subset(train,select = c(accommodates,cleaning_fee,review_scores_location,bathrooms,availability_30,availability_90,  calculated_host_listings_count_entire_homes,number_of_reviews_ltm,review_scores_value,calculated_host_listings_count,bedrooms,review_scores_rating,              minimum_minimum_nights,security_deposit,calculated_host_listings_count_shared_rooms,guests_included,review_scores_checkin,beds,                          host_listings_count,review_scores_cleanliness,maximum_minimum_nights,reviews_per_month,extra_people,availability_365,review_scores_accuracy                     ,host_identity_verified,availability_60,require_guest_phone_verification,number_of_reviews,minimum_nights,minimum_nights_avg_ntm,price))


#TEST DATA FEATURE SELECTION
sd_2 = subset(scoringdata,select = c(accommodates,cleaning_fee,review_scores_location,bathrooms,availability_30,availability_90,  calculated_host_listings_count_entire_homes,number_of_reviews_ltm,review_scores_value,calculated_host_listings_count,bedrooms,review_scores_rating,              minimum_minimum_nights,security_deposit,calculated_host_listings_count_shared_rooms,guests_included,review_scores_checkin,beds,                          host_listings_count,review_scores_cleanliness,maximum_minimum_nights,reviews_per_month,extra_people,availability_365,review_scores_accuracy                     ,host_identity_verified,availability_60,require_guest_phone_verification,number_of_reviews,minimum_nights,minimum_nights_avg_ntm))
```


```{r}
#TEST DATA IMPUTATION
scoringdata$host_is_superhost [is.na(scoringdata$host_is_superhost )]<-mean(scoringdata$host_is_superhost , na.rm = T)
scoringdata$host_total_listings_count[is.na(scoringdata$host_total_listings_count )]<-mean(scoringdata$host_total_listings_count , na.rm = T)
scoringdata$host_listings_count[is.na(scoringdata$host_listings_count )]<-mean(scoringdata$host_listings_count , na.rm = T)
scoringdata$security_deposit[is.na(scoringdata$security_deposit )]<-mean(scoringdata$security_deposit , na.rm = T)
scoringdata$cleaning_fee[is.na(scoringdata$cleaning_fee )]<-mean(scoringdata$cleaning_fee, na.rm = T)
scoringdata$beds[is.na(scoringdata$beds)]<-mean(scoringdata$beds, na.rm = T)
scoringdata$host_identity_verified[is.na(scoringdata$host_identity_verified )]<-mean(scoringdata$host_identity_verified, na.rm = T)
scoringdata$host_has_profile_pic[is.na(scoringdata$host_has_profile_pic )]<-mean(scoringdata$host_has_profile_pic, na.rm = T)
```



Model1 (Linear Regression)
```{r}
model1 = lm(price~bedrooms+bathrooms+beds+accommodates+guests_included+cleaning_fee+calculated_host_listings_count_entire_homes+calculated_host_listings_count_entire_homes+security_deposit,data=train)
```

Model 2 (Linear Regression)
```{r}
model2 = lm(price~.,data=train)
```
 
Model 3 (XGBOOST)

```{r}

library(xgboost)
library(vtreat)
set.seed(1031)
trt = designTreatmentsZ(dframe = train,varlist = names(train)[1:31])
names(train)[1:31]
newvars = trt$scoreFrame[trt$scoreFrame$code %in% c('clean','lev'),'varName']
train_input = prepare(treatmentplan = trt, 
                      dframe = train,
                      varRestriction = newvars)
test_input = prepare(treatmentplan = trt, 
                     dframe = scoringdata,
                     varRestriction = newvars)
library(xgboost)
xgboost = xgboost(data=as.matrix(train_input), 
                  label = train$price,
                  nrounds=57,
                  verbose = 0)

set.seed(1031)
tune_nrounds = xgb.cv(data =as.matrix(train_input), 
                      label = train$price,
                      nrounds=250,
                      nfold = 10,
                      verbose = 0)
ggplot(data=tune_nrounds$evaluation_log, aes(x=iter, y=test_rmse_mean))+
  geom_point(size=0.4, color='sienna')+
  geom_line(size=0.1, alpha=0.1)+
  theme_bw()
which.min(tune_nrounds$evaluation_log$test_rmse_mean)


```
Prediction
```{r}
pred = predict(xgboost,newdata=as.matrix(sd_2))
df = data.frame(id=scoringdata$id,price=pred)
write.csv(df,'submission045.csv',row.names=F)
```

